\input{title.tex}

### 2022-05-30 docs/papers/01_manuscript/04_discussion.tex
fix(output.docx,-version,-fix-figure-label.): fix figure caption, and output as a word version

\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
	\caption{
		\textbf{A.} The relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
	\label{fig:model}
\end{figure}

>>>>

\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
	\caption{
		The relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
	\label{fig:model}
\end{figure}
